---
output: github_document
--- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, eval = FALSE
)
```

# Evaluating Semi-Parametric Nowcasts of COVID-19 Hospital Admissions in Germany

This repository contains the documentation, results, and code of a project evaluating ... See the documentation for further details. 

## Citation

## Documentation

```{r, child = "docs/chunks/documentation.Rmd", eval = TRUE}
```

## Key files and folders

Folder/File | Purpose
---|---
[`writeup`](docs/) | Summary paper and additional supplementary information as `Rmarkdown` documents.
[`_targets.Rmd`](_targets.Rmd) | Analysis workflow for interactive use.
[`R`](R/) | R functions used in the analysis and for evaluation.
[`data`](data/) | Input data and summarised output generated by steps in the analysis.
[`.devcontainer`](.devcontainer/) | Resources for reproducibility using `vscode` and `docker`.

## Dependencies

Dependencies are managed using [`renv`].

Alternatively a docker [container](https://github.com/epiforecasts/simplfied-forecaster-evaluation/blob/main/.devcontainer/Dockerfile) and [image](https://github.com/epiforecasts/simplfied-forecaster-evaluation/pkgs/container/simplfied-forecaster-evaluation) is provided. An easy way to make use of this is using the Remote development extension of `vscode`.

## Analyses

